---
title: "Eating Out"
author: "ediaz16"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Who dines out more often?
There were two years in which the General Social Survey asked about the frequency of eating out. We look at one of them.

The variable name of interest is "eatout."  The URL is https://gss.norc.org/ In GSS data explorer look for "eatout." 

## Find those years 
For the first year the question was asked (1996) we have data. Your assignment is to analyze the GSS yearly data for 1996 and write a statistical report that answers the question.  The data are in the Files section.   

## introduction
$H_0$ There is no difference among the various races with regard to frequency of eating out  
$H_A$ There is a statistical difference between at least two races with rgard to the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source("fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
#require(haven)
GSS=read.csv('GSS1996.csv')

```

## Methods

Both 'race' and 'eatout' are categorical therefore we use the Cat~Cat helper file.

## Descriptive results

###graphical discription 

```{r}
barchartGC(~eatout + race,data=GSS)
barchartGC(~eatout + race,data=GSS, type="percent")


```

x axis is eatout(1=yes, 2=no) labels on the columes are (1=black,2=white,3=other)

White group they do not eat out.
###numerical description

```{r}
table= xtabs(~eatout+race, data=GSS)
print(table)
```

eating out race 1 more than not race 2 and 3 about the same eating out.

### Chi-squared test results

```{r}
chisq.test(table)
chisqtestGC(table)

```

There is no relationship in the chisq test. 

### fisherXY test results
```{r}
fisher.test(table)
fisherXY(GSS$eatout,GSS$race, printAll=T)
```

There is not difference among the varies races with regards eating out.

## Summary and Conclusions







